Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-05 doc/report/design.tex
added latex docs for the report, some graphs

Talks about the system design space.
What might be available to achieve such a function.

>>>>

% ok, I have to admit that when I start writing, I haven't figured out what to write.
% so kinda messy.

% this section is used to discuss the design considerations of the system
% starting from a motivating example, and then extract the key requireements, then about system design

In this section, we will talk about our thoughts on enabling direct interaction with physical device, driven by users' attention. We will first discuss one example application which motivates the work in this project. We also seek to summarize the key design requirements, and use them for the system design. Then several possible approaches are presented as an exploration o f the design space. To build a proof-of-concept system, we've simplified several tasks and implement a working system. The detailed implementation details will be covered in the next section.

\subsection{Example Application}
\label{sec:example-application}

Our work is primarily motivated by the observation that in CS294-84 course at Berkeley, the instructor has to go to the switch to turn off the light during presentation. The separation of device and their controller makes it possible for people control things that are not reachable (such as the lights on the ceiling). However, such indirection introduces additional overhead since people still need to locate the controller and then interact. Remote control might mitigate such problem, but again a controller for a device is not a scalable solution. Squeezing controllers into the smartphone display is also not the right approach. And these points will be more clear when we show our example application -- Smart Home.

% {\bf Smart Home}:
% Sean, maybe you can elaborate on this application more to motivate.
Imagine in a smart-home envinroment that most device are controllable remotely. When the users are watching TV shows, they want to turn off the lights and turn up the volume so they can enjoy this memorable time. Such ordinary-life tasks have been simplified so that they are able to issue ``turn off'' commands to the lights by simply staring at the light plus a specific gesture. Then they turn their head back to the TV, and again simply ``ask'' the TV to turn up the volume. When transitioning, the disconnection with lights and connection with TV happens seamlessly, with the correct feedback. Of course all the magic has to be resolved by an always-available device, such as glasses, rings, watches, or any other proper form factor. We will hold the discussion to the design space exploration.

Occasionally, the user needs to perform some advanced configuration to the TV, such as adjusting the white balance, or the brightness. Since the need of such complicated tasks are not frequent, and it will be less efficient to embed these features into the always-available device (which are designed to be small and easy-to-access, rather than too flexible). The smart-home falls back to a more generic approach which relies on touch screen or other rich input device. In this example case, since the user's attention is still on TV, his smartphone pops up the control menu for advanced usage automatically. Such menu could also just pop up on walls or other large interactive devices \cite{unPad:eWallpaper, MSVision}, but the attention-based interaction simplifies the selection on those flexible devices.

\subsection{System Requirements}
\label{sec:system-requirements}

From what we have described in the previous section, to achieve such direct interaction in attention, we have identified several key requirements.

% leads to the adoption of glass
The first and foremost is the ability of always-available sensing and acutation. Since our target is to simplify everyday task in smart-home/office scenario. Any cubersome solution is not desired.

Secondly, users are directly interacting with physical device. Since a screen is not always available, there should be some feedback indicator to explicit tell users what is going on.

As discussed before, we envision the simple always-available device would not be able to cover all tasks, especially some advanced ones. We will have to design the system to enable falling back.

For any human-centric system, additional requirements like responsiveness would aslo be required.

\subsection{System Design}
\label{sec:system-design}

In this section, we will present several design consideration that fulfills the requirements. From \cite{Merrill:2007:ALP:1758156.1758158}, they tried the solution of putting IR into earphones, rings to enable pointing metaphor. Other than that direction, recently published Google Glass project motivates us to consider glasses form factor. Glasses are natural in align with human's vision, and can reflect users' attention in a more precise way. But given the form factor of glasses, what might be a good approach to achieve sensing and actuation remains a challenge for us.

% kinda feel lost in describing

In our discussion, we've come up with three possible approaches. The first is a purely glass solution. The second is augmented by some computer vision detection. The third  will be a combination of glasses and smart watch.

% Lessons learned from \cite{Bellotti:2002:MSS:503376.503450} have also guided us in thinking the Five A's when designing novel interaction system.

### 2013-05-05 doc/report/implementation.tex
adding files to the report
added latex docs for the report, some graphs

\section{Evaluation}
\label{sec:evaluation}

>>>>

\section{Implementation}
\label{sec:implementation}

In this section, we details our implementation on Arduino \cite{Arduino} platform. The whole system is comprised of a glass module, numbers of clients, and a gateway. We will start by the clients, for which we only implement the simpliest functionalities. We push the burden of coordination to the glass.

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. In our current system, we have a relay which can control the AC power plug, and we have a USB connected computer to control video playing.

The main function of client is to respond IR signal, and communicate with glass to receive corresponding commands. When there is no glass initiating connection, the client simply lives in {\it IDLE} mode; while when they receive IR signal, indicating the user is expressing interest in interacting with it, the client responds with an XBee acknowledgement and goes into {\it PENDING} state. In this case, since the client doesn't know how many other clients have also responded to the glass, it will wait until a connection signal. If there are multiple clients waiting to be verified, the glass will coordinate all of them by sending the right verifying message. The active client that is being verified will blink faster, as visual feedback to users. When it receives the connection message, it goes to {\it CONNECTED} state and is ready to take commands. To summarize the behavior, we have a state machine in Fig.\,\ref{fig:clientFSM} for illustration.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{../figs/clientFSM.pdf}
  \caption{FSM model for client}
  \label{fig:clientFSM}
\end{figure}

Within {\it CONNECTED} state, the clients' behaviors are different from each other according to the device it is connected to. In our prototype, we have two different types of devices. The first is a relay, which can then control the whole AC power supply. To control the relay, we only need to set a digital pin to {\it LOW} or {\it HIGH}, and each action is encoded in the command set from the glass. The second is a computer that is used to play video. And the direct interaction includes adjusting the volume and pause/play. These commands are sent to the computer through USB serial data.

\subsection{Glass}
\label{sec:glass}

The Glass is complicated in two folds. First, we move the complexity of coordinating all clients to the Glass. Second, we have to handle user gesture on Glass.

% add graphs and FSM for Glass

\subsection{Gateway}
\label{sec:gateway}

The gateway provides access to the personal area network for computers, and presumably this can be further open to the Internet. Since there have already been many products \cite{NinjaBlocks, Lockitron} that essentially function in this way, we do not spend much time on this aspect in our project.

### 2013-05-05 doc/report/intro.tex
added latex docs for the report, some graphs

>>>>

In comparison, taking out the phones (or even simply locating them) is relatively time-consuming. According to a study in \cite{Ashbrook:2008:QIM:1357054.1357092}, 4 seconds are required on average just to get a phone out of the pocket or hip holster, not to mention the time to choose the target and initiate interaction.
